Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-01 prob.tex
prob.tex \section{Proofs} thm:analogTheorem21RichmanBridges1999 Briefly proved...

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. Let $a$ be the difference in longitudes
of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{Double check how many step at least from $\ket{\psi'}$ to a point
$\ket{\psi_{s}}$.}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be typed...},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}
\begin{itemize}
\item Let $f$ be a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}\le\eta+g\left(\ket{\psi}\right)\le W_{r}$ for all
$\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.

@@

For any point $\ket{\psi}$ in the closed northern hemisphere, consider

For each $\varphi$ define $F_{\varphi}$ on $\left[0,1\right]$ by
setting $F_{\varphi}\left(\ell\left(\ket{\psi}\right)\right)=W-g\left(\ket{\psi}\right)$
where $\ket{\psi}$ is a point in the closed northern hemisphere with
longitude~$\varphi$. Then, $\left|F_{\varphi}\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|\le2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$
\end{proof}

>>>>

\begin{lemma}\label{lemma:analogLemma20RichmanBridges1999}If $f$
is a nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\eta=f\left(\ket{0}\right)$, then the oscillation on any latitude
of the symmetrization of $f$ with respect to $\ket{0}$ is at most
$\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
The exact $n$ could be computed to minimize the oscillation when
the function $f$ is given.\qed\end{lemma}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Let $g$ be
the symmetrization of $f$ with respect to $\ket{0}$, then $\omega_{g}\left(\delta\right)=2\omega_{f}\left(\delta\right)$.
Let $\ket{\psi}$ and $\ket{\psi'}$ be points in the northern hemisphere
with the same latitude~$\theta$. Let $a$ be the difference in longitudes
of $\ket{\psi}$ and $\ket{\psi'}$. Take $n$ steps along east-west
great circles to go from $\ket{\psi'}$ to a point $\ket{\psi_{s}}$
due south of $\ket{\psi}$\footnote{\yutsung{Double check how many step at least from $\ket{\psi'}$
to a point $\ket{\psi_{s}}$.}}. The difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, while, from Lemma \footnote{\yutsung{Analog to Lemma 16 in \cite{RichmanBridges1999}... To be
typed...}},
\[
g\left(\ket{\psi_{s}}\right)\ge g\left(\ket{\psi'}\right)-n\left[2f\left(\ket{0}\right)+4\left(W_{r}-W_{l}\right)\right]=g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)\textrm{ .}
\]
When the difference in latitude between $\ket{\psi}$ and $\ket{\psi_{s}}$
is at most $\frac{a^{2}}{n}$, the length between $\ket{\psi}$ and
$\ket{\psi_{s}}$ is at most $2-2\cos\left(\frac{a^{2}}{n}\right)$,
and hence 
\[
g\left(\ket{\psi}\right)\ge g\left(\ket{\psi_{s}}\right)-\omega_{g}\left(2-2\cos\left(\frac{a^{2}}{n}\right)\right)\ge g\left(\ket{\psi'}\right)-2n\eta-4n\left(W_{r}-W_{l}\right)-2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)
\]
for $\frac{\pi^{2}}{n}\le\frac{\pi}{2}\Leftrightarrow2\pi\le n$.\footnote{\yutsung{We are going to verify this proof by set $W_{r}-W_{l}=0$.
Since $f$ is continuous in this case, we could solve $n\ge2\pi$
such that $2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)\le\frac{\delta}{2}$
for any $\delta>0$, and then solve $\eta\ge0$ such that $2n\eta\le\frac{\delta}{2}$.}}
\end{proof}
The following theorem is an analog to Theorem~21 in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}} nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g\left(\ket{\psi}\right)\le W_{r}-\eta$ for
all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.

@@

For any point $\ket{\psi}$ in the closed northern hemisphere, consider
its longitude~$\varphi$, and a function~$F\left(a\right)=W-g\left(\ket{\psi'}\right)$,
where $\ket{\psi'}$ is a point in the closed northern hemisphere
with longitude~$\varphi$, and $a=\ell\left(\ket{\psi'}\right)$.
More specifically, let $\ket{\psi_{i}'}$ be a point in the closed
northern hemisphere with longitude~$\varphi$ such that $a_{i}=\ell\left(\ket{\psi_{i}'}\right)$.
Hence, $\ket{\psi_{i}'}$ and $\ket{\psi_{i}}$ are in the same latitude
so that 
\[
\left|F\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|=\left|g\left(\ket{\psi_{i}}\right)-g\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
\]
for all $i$. Whence, 
\begin{eqnarray*}
 &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
 & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right)\right|\\
 & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
 & \le & 3\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
\end{eqnarray*}
Therefore, by Lemma~19 in \cite{RichmanBridges1999}, 
\[
\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|W-g\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
\]
\end{proof}
